# My Chapter Title

## Introduction

Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again. Here we go again.

## Methods

This is how I did the thing

See Table \@ref(tab:testtable-3)

```{r testtable-3, fig.scap="Summary of the mtcars data."}
data("mtcars")
knitr::kable(summary(cars), caption = "Summary of the mtcars data. Sentence two.", caption.short="Summary of the mtcars data.")
# For multi-sentence sentence captions use caption.short for list of tables version of caption (first sentence) 
```

## Results

These are more results (Figure \@ref(fig:cars-plot-2)). Cross-referencing this figure is possible thanks to the bookdown package [@xie2016bookdown] and we can use the visual markdown editor from Rstudio to make writing in markdown easier [@allaire2012rstudio].

```{r cars-plot-2, fig.cap="The cars data2."}
plot(cars)  # a scatterplot
```

Let's reference figure \@ref(fig:cars-plot) from chapter 1 from chapter 2. And now let's reference some extra stuff contained in the appendix (Figure \@ref(fig:iris-data-fig)).

### An Equation and some math

```{=tex}
\begin{equation}
  Y=mx+b 
  (\#eq:line)
\end{equation}
```
Inline math example: $1+1=2$

Display math example:

$$
2+2=4
$$

This is the equation of a line Equation \@ref(eq:line)

## Discussion

Now I tell you how this fits in the context of my field.
